The powder x-ray diffractogram open database

### 2024-04-29 paper/01_introduction.tex
Weakened the statement about translating neural networks performance on data stemming from experiment

Models trained on datasets with simulated diffractograms have already shown very strong performance in predicting
lattice parameters, spacegroup and crystallite size from simulated diffractograms but the performance drops off immensely
when these models are applied to data originating from experiment.
There is every reason to believe, that the strong performance observed in the domain of purely simulated diffractograms
can translate to predicting crystal structure properties of diffractograms originating from experiment, given that
models are trained on a dataset that accurately reflects diffractograms as they appear in experiment. \\

>>>>

Models trained on datasets with simulated diffractograms have already shown very strong performance in predicting
lattice parameters, spacegroup and crystallite size from simulated diffractograms but the performance drops off immensely when these models are applied to data originating from experiment.

The patterns observed in experiment suffer from a host of imperfections that may result in a partial loss of information or make extracting the structural information more difficult. \\
However, there is still reason to believe that the strong performance observed in the domain of purely simulated diffractograms can to a large extent translate to predicting crystal structure properties from diffractograms originating from experiment, given that models are trained on a dataset that accurately reflects diffractograms as they appear in experiment.
